Autonomous Realization of Simple Machines

### 2014-05-27 doc/paper/paper.tex
shrinked images to save file sizes and 'finished' results. next: clean up the paper to make room for discussion

\newpage
\section{Technical Approach}

@@

\vspace{-2em}
\subsubsection{Guarded and conformant motions}

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/short.png}
  \caption{.}
  \label{fig:short}
\end{figure}

@@

We offer two insights from our experiments. First, the manipulation of heavy objects brings about
interesting challenges. If the object inertia model is not known, the system can be thrown off
balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
start spinning since one wheel has to accommodate the extra weight.

\newpage
% \bibliographystyle{unsrt}
% \bibliography{references}

@@

@@

% DISCUSSION: CHALLENGES WITH VISUAL SERVOING A NONHOLONOMIC ROBOT BASE

>>>>

\section{Technical Approach}

@@

\subsubsection{Guarded and conformant motions}

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/short.png}
  \caption{The movement of the fulcrum-lever contact point for short lever objects.}
  \label{fig:short}
\end{figure}

@@

The manipulation of heavy objects brings about interesting challenging in manipulation, locomotion
and control fields. First of all, even though the mass and the center of mass information of a
carried load is sufficient in maintaining quasi-static balance, the inertias are needed when
the motion become faster. Although most of the time, the dynamic parameters of manipulated objects
is not readily available, there are a variety of methods to estimate them with simple experiments
\cite{saal2010active} or with simplifying assumptions based on geometry and mass.

Secondly, we observe that the configuration of the grasped object with respect to the body frame
can affect the accuracy of locomotion. For instance, carrying a 15 kg load in the middle of the 
two wheels as opposed to a meter off to the side induces different output trajectories for the 
same velocity profiles. Figure \ref{fig:wheels} demonstrates the effect of the distribution 
of the load mass over the wheels where the robot moves a cinder block from +1 meter to the -1 meter off
its center and attempts to follow a straight line. The results show a proportional relationship
where the trajectories bias towards the load increases with the distance between the load and the center. 
We speculate that the cause is that the wheel with the more weight on has to apply more torque
to keep up with the other one. Note that the distribution of the load and its effect of the joint
torques is a general issue that also affects legged humanoid robots.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/wheels.png}
  \caption{The effect of the grasping location on the accuracy of locomotion.}
  \label{fig:wheels}
\end{figure}

Lastly, the mass and the sheer size of the manipulated objects can cause problems with robust
grasping during locomotion. For instance, for Golem Krang's grippers with two prismatic finger joints,
it is important to guarantee that an object would not slip from its grasp as the robot turns around
swiftly. To handle such cases, we have adopted a two-hand grasp for the cinder block and ensured
that the lever is held mostly from its middle region and at an upwards angle.

\section{Discussion}

@@

\bibitem{saal2010active} Saal, H. P., Ting, J. A.,  Vijayakumar, S.: Active estimation of object dynamics
parameters with tactile sensors. IROS, 2010. 

@@

% DISCUSSION: CHALLENGES WITH VISUAL SERVOING A NONHOLONOMIC ROBOT BASE
% Lastly, we observe that the manipulation of multiple objects to assemble functional structures
% is closely related to the grasp problem where the manipulator has to choose how to grasp the objects.
% In this work, we use predetermined grasp areas for the cinder block and the planner is provided
% the orientation of the hand as the robot grasps the lever. Moreover, learning from the effect
% of the carried load configuration on locomotion, we adopt an atomic behavior that holds the load
% in the middle of the robot.
